\vskip-0.6in \Large Political Uncertainty

### 2015-03-23 GS-extension.tex
add non-negativity constraint on b(j)

							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B

@@

>>>>

							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j

@@

										\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
										\item Some legislators who are past FOC point will not be lobbied
